\vspace{-5em}\Huge Generation of a Synthetic Population and Travel Network for an Agent Based Traffic Simulation

### 2023-08-05 paper/paper.tex
Small typo in paper

    \quad Fortunately, nowadays, traffic simulation has started to move in the direction of agent based models \cite{ile-de-france}. These models function on a lower level, looking at the activities of people and their interactions \cite{agent-based-model}. However, in order to compute such specific predictions about a population, a lot of input data is required. Similar to any form of a simulation, you can't create information, just analyze it. Thus, the accuracy of the traffic demand determines the accuracy of the output. The best way to go about solving this problem is by sampling large populations down to an accurate, but still computable size. Still, very few governments openly release sufficient data about their populations for traffic modeling. One example, can be seen in France, where an open-source pipeline was created for this exact scenario of sampling \cite{ile-de-france}. The pipeline uses stochastic\footnote{Use of random probability to determine a quantity} models, such as the Monte Carlo simulation to sample an even size of the data of the France. In their case, the model results in data that is just 5\% of the size of Île-de-France's population. Having such a tool allows researchers to analyze existing traffic flows through agent based simulations, such as MATSIM\footnote{Open source framework for implementing agent based transport simulations} \cite{matsim}.\\

>>>>

    \quad Fortunately, nowadays, traffic simulation has started to move in the direction of agent based models \cite{ile-de-france}. These models function on a lower level, looking at the activities of people and their interactions \cite{agent-based-model}. However, in order to compute such specific predictions about a population, a lot of input data is required. Similar to any form of a simulation, you can't create information, just analyze it. Thus, the accuracy of the traffic demand determines the accuracy of the output. The best way to go about solving this problem is by sampling large populations down to an accurate, but still computable size. Still, very few governments openly release sufficient data about their populations for traffic modeling. One example, can be seen in France, where an open-source pipeline was created for this exact scenario of sampling \cite{ile-de-france}. The pipeline uses stochastic\footnote{Use of random probability to determine a quantity} models, such as the Monte Carlo simulation to sample an even size of the data of France. In their case, the model results in data that is just 5\% of the size of Île-de-France's population. Having such a tool allows researchers to analyze existing traffic flows through agent based simulations, such as MATSIM\footnote{Open source framework for implementing agent based transport simulations} \cite{matsim}.\\
